Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages

### 2015-09-10 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
minor

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences}
\title{Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages}

@@

\begin{abstract}
%\boldmath
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) which types of constraint languages are able to express their type of constraint. We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic sciences obtained from 33 SPARQL endpoints.
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioural, and economic (SBE)} sciences and represents them in the W3C group.

@@

In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages. All in all, this lead to 115 constraints on three vocabularies
We let the experts classify the constraints according to the severity of their violation. Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter \ref{classification}).

As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data on three common vocabularies in SBE sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulate several findings to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
these findings still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the SBE domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the SBE domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the SBE community (section \ref{motivation}), 
%how data in tabular format and metadata on unit-record data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how SBE (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the SBE domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioural, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL. 
Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Aspects of RDF Data Constraints in the Social, behavioral, and Economic Sciences}
\title{Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages}

@@

\begin{abstract}
%\boldmath
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) which types of constraint languages are able to express their type of constraint. We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic sciences obtained from 33 SPARQL endpoints.
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C group.

@@

In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages. All in all, this lead to 115 constraints on three vocabularies.
We let the experts classify the constraints according to the severity of their violation. Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter \ref{classification}).

As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data on three common vocabularies in SBE sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulate several findings to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
these findings still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the SBE domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the SBE domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the SBE community (section \ref{motivation}), 
%how data in tabular format and metadata on unit-record data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how SBE (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the SBE domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL. 
Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.
